### 2024-08-13 getting-started.qmd
20240812 - load data to fix error
20240812 - create a vector and list

@@

Here is an example of creating a data frame:

@@

>>>>

## Create a Vector {#sec-createVector}

A vector is a series of elements that can be numeric or character.
It has one dimension (length).
To create a vector, use the `c()` to combine elements into a vector:

```{r}
exampleVector <- c(40, 30, 24, 20, 18, 23, 27, 32, 26, 23, NA, 37)
```

@@

A data frame has two dimensions: rows and columns.
Here is an example of creating a data frame:

@@

## Create a List {#sec-createList}

A list can store multiple data frames in one object:

```{r}
exampleList <- list(players, fantasyPoints, fantasyPoints_weekly)
```

## Load a Data Frame {#sec-gettingStartedLoadData}

```{r}
load(file = "./data/nfl_players.RData")
```
